\documentclass[tom-jenni]{subfile}
\begin{document}
	
	\chapter[2D]{\di2}
	
Our \di2 opener is somewhat similar to our \cl2 opener, but weaker. The nominal range for \di2 is 9--12, but some 12s are going to be too good and some 8s will likely be upgraded. The structure here is similar in nature to \cl2. Most NF bids have been bumped 1 HCP.

\begin{bidtable}{\orauction{2d}}      
	\he2 & Artificial asking bid, promising INV+ \\
	\sp2 & NF constructive, usually about 8--12 HCP, 5+ \sss \\
	2NT & NF constructive in \ccc ~or \hhh. \cl3 is pass or correct, \di3 suggests no interest in playing in \ccc; says nothing about \hhh. \\
	\cl3 & Puppet to \di3, showing either a weak raise in \ddd (most common) or a GF 5+ 5+ hand without \ddd. \\
	\di3 & Constructive up to a mild invite, usually around 9--12 \\ 
	\he3/\sp3/\cl4 & Nat, 6+ card suit, GF. \\
	3NT & To play. \\
	\cl4 & RKC \ddd \rem{CIRKLE?} \\ 
	\di4 & Preemptive \\
	\he4/\sp4 & To play. \\
\end{bidtable}

\begin{bidtable}{\orauction{2d,2h}}
	\sp2 & 4 cards in either major. 2NT asks, \hhh~min/\sss~min/\hhh~max/\sss~max. \\
	2NT & Maximum, interest in declaring NT. Bal or \shape{6331} with stiff K. \\
	\cl3 & Maximum, no 4-card major, unbalanced or unsuitable for declaring NT. \\
	\di3 & Minimum, no 4-card major. \\
	& Higher bids are undefined. \\
\end{bidtable}

\di2--\he2--\cl3--\he3 asks for shortness, NLMH. \rem{Awkward but symmetrical.}

\begin{noted}[2NT and then?]
	Had a funny sequence come up in the JLall.  \di2--2NT--\cl3--\di4.  Ari was \exactshape{2137} and was trying to invite based on the club tolerance.  Tom wasn't sure what was going on and with \exactshape{1363} bid \he4 to cater to both suit possibilities.  Ari corrected to \di5 (probably should have been \cl5 instead) and we made it with a bit of luck.
\end{noted}
	
\end{document}



