\documentclass[tom-jenni]{subfile}
\begin{document}
	
	\chapter{2NT}
	
	22--23 balanced or whatever passes for it these days.
	
	Responses:
	
	\begin{bidtable}{\orauction{2n}}
		\cl3 & Extended Stayman \\
		\di3 & Xfer \\
		\he3 & Xfer \\ 
		\sp3 & Puppet to 3NT for minor suit hands. \\
		3NT & To play \\
		\cl4 & 1430 Gerber \\
		\di4 & Xfer \\
		\he4 & Xfer \\
		\sp4 & Both minors balanced (typically 4-4), quant or better. \\
		4NT & Quant. New suits are 5+ card suits. \\
		5NT & Forcing, invites 7. New suits are 5+ card suits.
	\end{bidtable}

\section{Stayman Agreements}

\rem{Some of this may be new to you, I don't recall if I've talked about this at all. See \sp3 and 3NT responses as well as \he3 extensions.}

	\begin{bidtable}{\orauction{2n,3c}}
		\di3 & No 4 card major. 3M rebid over this is Smolen. 4m is natural and forcing. There are no delayed Texas type sequences directly, go through Smolen. \\
		\he3 & 4+ \hhh. \sp3 asks about heart length and/or is a \hhh~ slam try. Opener bids 3NT with only 4, (over which a new suit is a cuebid slam try for \hhh) or bids \he4 or cuebids a minor with 5 \hhh. Responder doesn't promise a slam try, they can simply be trying to confirm a 5 card suit. \\
		\sp3 & 4 \sss. \he4 agrees \sss~ with slam interest, \cl4/\ddd~ are natural (not cuebids). \\
		3NT & 5 \sss. \he4\rightarrow\sp4 (with or without slam interest), \cl4/\ddd~ are natural. \\
	\end{bidtable}

\section{Transfer Agreements}

\he3 then \he4 shows 5-5 majors without slam interest.
\di3 then \sp3 shows 5-5 majors with slam interest.

4m rebids are natural and forcing.

Jacoby then 4NT:  Quant
Texas than 4NT:  RKC (1430)
Texas than new suit: Exclusion (0314)

\section[3S]{\sp3}

Puppet to 3NT for minor suit hands.

\begin{bidtable}{\orauction{2n,3s,3n}}
	\cl4 & \ddd. Responder bids next step (\di4) with any hand that doesn't like the idea of slam, otherwise responds RKC for \ddd. \\
	\di4 & \ccc. Responder bids next step (\he4) with any hand that doesn't like the idea of slam, otherwise responds RKC for \ccc. \\
	4M & Shortness in bid M, 5-5 minors with slam interest. \\
	4NT & 5-5 minors with no slam interest. \\
\end{bidtable}

If opener bids a ``don't like'' step, +1 is ``don't care, RKC.'' 4NT by responder is NF.

\end{document}
