\documentclass[tom-jenni]{subfile}
\begin{document}

\chapter{Introduction}

Attempting to write an up-to-date ``TaJ'' system without the Tom/Ari ++ extensions.  This document likely will be used by Jenni and Greg.

The latest version of this file should be available at \url{https://github.com/tomc/jenni/blob/master/tom-jenni.pdf}

\section{Versions}

\subsection{March 2022}

\begin{itemize}
	\item \di1 is now 2+ in \third seat, still 0+ in others.
	\item Reverse Flannery responses to \di1 have been replaced with natural and invitational jumps.
	\item 1M--3M is weak, 1M--2NT is mixed both in comp and directly.
	\item \di1--(Dbl)--\sp2 is Nat Inv 6+, with \he2 = weaker or stronger.  2NT is now the mixed both minors bid.
	\item Optional RKC in relay auctions after the relays have completed and the auction is below 3NT.
	\item 1M--\cl2 is a general GF, it includes the balanced hands.  The responses have not changed, but the 2NT rebid by Responder is now just showing a balanced hand, not both minors.
	\item \he1--\sp2 is Nat Inv.  Not sure if this is a change in the notes, so commenting here in case.
	\item 1NT--(2x)--Dbl is now takeout/negative, not penalty.  (Assuming 2x is natural)
	\item Rusinow leads vs Suits when 4+ cards are promised.  Applies to both sides if they have promised that much length, e.g. both \he1--(Dbl)--\he3--(\sp3) and \he1--(\sp1)--\he3--(\sp3).
	\item Light text edits for clarity.
\end{itemize}

\subsection{2021 and earlier}

Most notable changes are:

\begin{itemize}
	\item TaJ Relay has been updated to have the first step be all 5-4 hands.  This alleviates the need for some of the awkward \cl1 resposnes and allows us to revert to playing the semi-positives we prefer.
	\item 2 level responses to \di1 are all changed.  \cl2/\ddd are now both natural and forcing with \he2/\sss being reverse Flannery responses. \cl3/\ddd are both mixed.
\end{itemize}

\section{Notation}

\begin{description}
	\item[R] Simple Raise
	\item[R+1] One above a simple raise
	\item[DR] Double Raise
	\item[TR] Triple Raise
	\item[LMH] Low-Middle-High
	\item[LHB] Low-High-Both (Shortness relay after 10+ known cards.)
	\item[+1] Next Bidding Step
	\item[M] Major.  If one has been shown, it is the same one.
	\item[OM] Other Major.  After a major is shown.
	\item[m,om] Minor, other minor.
	\item[JS] Jump Shift
	\item[DJS] Double Jump Shift
	\item[UTL] Up The Line (\ccc\ddd\hhh\sss)
	\item[OKC] Optional Key Card
\end{description}


\end{document}